GPU Efficient Texture Based Bezier Curve Evaluation

### 2015-08-27 Submission/PaperSource/paper.tex
Submitted!

%-------------------------------------------------------------------------
\section*{Index of Supplemental Materials}
\label{sec:indexofsupplementalmaterials}
TODO: put information about where the zip can be downloaded.

The zip file contains a folder named WebGL which contains the WebGL demos, and a folder named GLFW which contains the GLFW (windows) C++ OpenGL demos.

@@

\paragraph{\textbf{GLFW Folder}}
\begin{itemize}
  \item \textit{Curves} --- The folder that contains the source code and the project and solution file for the demos.
  \item \textit{glew-1.12.0} --- The glew library used for the demos.
  \item \textit{glfw-3.1.1} --- The glfw library used for the demos.  
\end{itemize}

>>>>

%-------------------------------------------------------------------------
\section*{Index of Supplemental Materials}
\label{sec:indexofsupplementalmaterials}
The zip file contains a folder named WebGL which contains the WebGL demos, and a folder named OpenGL which contains the C++ OpenGL demos.

@@

\paragraph{
\textbf{OpenGL Folder}
\newline
This folder contains the source code, project and solution file for the C++ OpenGL demos.  The demos were created using the libraries glew-1.12.0 and glfw-3.1.1.
}
